Variation generation and mean fitness increase: \\ Necessity is the mother of genetic invention

### 2017-11-14 ms.tex
acks for LA

% Migration model
\paragraph*{Migration model.}\label{sec:mig_model_1}

@@

This research was supported in part by the Stanford Center for Computational, Evolutionary and Human Genomics, and by the Morrison Institute for Population and Resources Studies, Stanford University.
}

>>>>

% Migration model 1
\paragraph*{Migration model 1.}\label{sec:mig_model_1}

@@

This work was supported in part by the Department of Information and Computer Sciences at the University of Hawai`i at M{\=a}noa, the Konrad Lorenz Institute for Evolution and Cognition Research, the Mathematical Biosciences Institute through National Science Foundation Award \#DMS 0931642, the Stanford Center for Computational, Evolutionary and Human Genomics, by the Morrison Institute for Population and Resources Studies Stanford University.
}
